### 2016-10-03 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Added Durock name in construction section

\vspace*{2\baselineskip}
September 2016}

@@

The first floor interior walls of each structure were framed with steel studs set to 400~mm (16~in) centers and track. Two layers of 16~mm (0.63~in) Type X gypsum board lined the steel studs, and a layer of 13~mm (0.5~in) thick cement board covered the gypsum board. The interior ceiling of each structure was covered by two layers of 13~mm (0.5~in) thick cement board.
\FloatBarrier

@@

\subsubsection{Second Floor of West Structure}
The second floor of the West Structure was built on the structure's first floor wood ceiling support. The two floors were connected by an interior stairwell. A door made of lauan plywood was located at the top of the stairwell. The walls on the second floor were of wood-frame with 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers. Two layers of 16~mm (0.63~in) Type X gypsum board lined the interior side of the wood studs, and a layer of 13~mm (0.5~in) thick cement board covered the gypsum board. The interior ceiling of the second story was covered by two layers of 13~mm (0.5~in) thick cement board. The exterior sides of the outer walls on the second floor were protected by 11~mm (0.44~in) thick OSB and 8~mm (0.31~in) fiber cement lap siding.

@@

\subsubsection{Gas Sampling}
A gas sampling system with relative expanded uncertainty of $\pm$1~\% when compared to span gas volume fractions~\cite{Bundy:2007} from California Analytical Instruments, Inc. (model 602P) was used to make gas concentration measurements. However, according to a study by Lock~et~al.~\cite{Lock:1}, the non-uniformity and movement of exhaust gases contribute to an estimated relative expanded uncertainty of $\pm$12~\%.

>>>>

\vspace*{2\baselineskip}
October 2016}

@@

The first floor interior walls of each structure were framed with steel studs set to 400~mm (16~in) centers and track. Two layers of 16~mm (0.63~in) Type X gypsum board lined the steel studs, and a layer of 13~mm (0.5~in) thick Durock cement board covered the gypsum board. The interior ceiling of each structure was covered by two layers of 13~mm (0.5~in) thick Durock cement board.
\FloatBarrier

@@

\subsubsection{Second Floor of West Structure}
The second floor of the West Structure was built on the structure's first floor wood ceiling support. The two floors were connected by an interior stairwell. A door made of lauan plywood was located at the top of the stairwell. The walls on the second floor were of wood-frame with 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers. Two layers of 16~mm (0.63~in) Type X gypsum board lined the interior side of the wood studs, and a layer of 13~mm (0.5~in) thick Durock cement board covered the gypsum board. The interior ceiling of the second story was covered by two layers of 13~mm (0.5~in) thick Durock cement board. The exterior sides of the outer walls on the second floor were protected by 11~mm (0.44~in) thick OSB and 8~mm (0.31~in) fiber cement lap siding.

@@

\subsubsection{Gas Sampling}
A gas sampling system from California Analytical Instruments, Inc. (model 602P) having a relative expanded uncertainty of $\pm$1~\% when compared to span gas volume fractions~\cite{Bundy:2007} was used to make gas concentration measurements. However, according to a study by Lock~et~al.~\cite{Lock:1}, the non-uniformity and movement of exhaust gases contribute to an estimated relative expanded uncertainty of $\pm$12~\%.
